---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Results

## Summary | To be completed!

The following table give global information on datasets.

```{r}
Seurat_object_list <- list(Seurat_UPN23, Seurat_UPN29, Seurat_UPN23_UPN29_cellhashing_UPN23, Seurat_UPN23_UPN29_cellhashing_UPN29, Seurat_UPN73, Seurat_UPN78, Seurat_UPN73_UPN78_cellhashing_UPN73, Seurat_UPN73_UPN78_cellhashing_UPN78)

# table_colnames <- c("Estimated number of cells", "Mean reads per cell", "Median genes per cell", "Sequencing saturation", "Read mapped confidently to genome", "Fraction reads in cells", "Total genes detected", "Median UMI counts per cell")
# Result_table <- data.frame(matrix(nrow = 8, ncol = 8), row.names = c("UPN23", "UPN29", "UPN23_cellhashing", "UPN29_cellhashing", "UPN73", "UPN78", "UPN73_cellhashing", "UPN78_cellhashing"))
# colnames(Result_table) <- table_colnames
# Result_table$`Estimated number of cells` <- sapply(Seurat_object_list, ncol)
# Result_table$`Median genes per cell` <- sapply(Seurat_object_list, function(x){median(x$nFeature_RNA)})
# DT::datatable(Result_table)
```

## Some QC plots for each sample

On the following plots, the sample is indicated in X axis.

Those plots show the distribution of the number of UMI (nUMI), the number of genes (ngenes) and the percentage of mitochondrial genes (percent_mito) in each cell (dot on plots).

### UPN23

```{r QC_UPN23}
Seurat_UPN23 <- compute_percent_mito_seurat(Seurat_UPN23)
draw_QC_plots_seurat(Seurat_UPN23)
draw_QC_plots_seurat_no_dots(Seurat_UPN23)

draw_all_qc_plot_with_outlier(Seurat_UPN23, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN23_filtered <- subset(Seurat_UPN23, subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                invert = T)
```

### UPN29

```{r QC_UPN29}
Seurat_UPN29 <- compute_percent_mito_seurat(Seurat_UPN29)
draw_QC_plots_seurat(Seurat_UPN29)
draw_QC_plots_seurat_no_dots(Seurat_UPN29)

draw_all_qc_plot_with_outlier(Seurat_UPN29, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 20)
Seurat_UPN29_filtered <- subset(Seurat_UPN29, subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                invert = T)
```

### UPN23 with cellhashing

```{r QC_UPN23_cellhashing}
Seurat_UPN23_UPN29_cellhashing_UPN23 <- compute_percent_mito_seurat(Seurat_UPN23_UPN29_cellhashing_UPN23)
draw_QC_plots_seurat(Seurat_UPN23_UPN29_cellhashing_UPN23)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_UPN29_cellhashing_UPN23)

draw_all_qc_plot_with_outlier(Seurat_UPN23_UPN29_cellhashing_UPN23, filter_numi = 20000, 
                              filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN23_UPN29_cellhashing_UPN23_filtered <- subset(Seurat_UPN23_UPN29_cellhashing_UPN23, 
                                                        subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                                        invert = T)
```

### UPN29 with cellhashing

```{r QC_UPN29_cellhashing}
Seurat_UPN23_UPN29_cellhashing_UPN29 <- compute_percent_mito_seurat(Seurat_UPN23_UPN29_cellhashing_UPN29)
draw_QC_plots_seurat(Seurat_UPN23_UPN29_cellhashing_UPN29)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_UPN29_cellhashing_UPN29)

draw_all_qc_plot_with_outlier(Seurat_UPN23_UPN29_cellhashing_UPN29, filter_numi = 20000, 
                              filter_ngenes = 4000, filter_percent_mito = 20)
Seurat_UPN23_UPN29_cellhashing_UPN29_filtered <- subset(Seurat_UPN23_UPN29_cellhashing_UPN29, 
                                                        subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                                        invert = T)
```

### UPN73 fixed

```{r QC_UPN73}
Seurat_UPN73 <- compute_percent_mito_seurat(Seurat_UPN73)
draw_QC_plots_seurat(Seurat_UPN73)
draw_QC_plots_seurat_no_dots(Seurat_UPN73)

draw_all_qc_plot_with_outlier(Seurat_UPN73, filter_numi = 20000, 
                              filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN73_filtered <- subset(Seurat_UPN73, subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                invert = T)
```

### UPN78 fixed

```{r QC_UPN78}
Seurat_UPN78 <- compute_percent_mito_seurat(Seurat_UPN78)
draw_QC_plots_seurat(Seurat_UPN78)
draw_QC_plots_seurat_no_dots(Seurat_UPN78)

draw_all_qc_plot_with_outlier(Seurat_UPN78, filter_numi = 20000, 
                              filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN78_filtered <- subset(Seurat_UPN78, subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                invert = T)
```

### UPN73 cellhashing

```{r QC_UPN73_cellhashing}
Seurat_UPN73_UPN78_cellhashing_UPN73 <- compute_percent_mito_seurat(Seurat_UPN73_UPN78_cellhashing_UPN73)
draw_QC_plots_seurat(Seurat_UPN73_UPN78_cellhashing_UPN73)
draw_QC_plots_seurat_no_dots(Seurat_UPN73_UPN78_cellhashing_UPN73)

draw_all_qc_plot_with_outlier(Seurat_UPN73_UPN78_cellhashing_UPN73, filter_numi = 20000, 
                              filter_ngenes = 4000, filter_percent_mito = 20)
Seurat_UPN73_UPN78_cellhashing_UPN73_filtered <- subset(Seurat_UPN73_UPN78_cellhashing_UPN73, 
                                                        subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                                        invert = T)
```

### UPN78 cellhashing

```{r QC_UPN78_cellhashing}
Seurat_UPN73_UPN78_cellhashing_UPN78 <- compute_percent_mito_seurat(Seurat_UPN73_UPN78_cellhashing_UPN78)
draw_QC_plots_seurat(Seurat_UPN73_UPN78_cellhashing_UPN78)
draw_QC_plots_seurat_no_dots(Seurat_UPN73_UPN78_cellhashing_UPN78)

draw_all_qc_plot_with_outlier(Seurat_UPN73_UPN78_cellhashing_UPN78, filter_numi = 20000, 
                              filter_ngenes = 4000, filter_percent_mito = 20)
Seurat_UPN73_UPN78_cellhashing_UPN78_filtered <- subset(Seurat_UPN73_UPN78_cellhashing_UPN78, 
                                                        subset = ngenes_filter & nUMI_filter & percent_mito_filter,
                                                        invert = T)
```

```{r}
# Clean memory
rm(Seurat_object_list, Seurat_UPN23, Seurat_UPN29, Seurat_UPN23_UPN29_cellhashing_UPN23, Seurat_UPN23_UPN29_cellhashing_UPN29, Seurat_UPN73, Seurat_UPN78, Seurat_UPN73_UPN78_cellhashing_UPN73, Seurat_UPN73_UPN78_cellhashing_UPN78)
gc()
```

