---
output: html_document
editor_options: 
  chunk_output_type: console
---

### Comparison od DE genes for each sample.

#### UPN23 

```{r}
UPN23_non_cellhashing_unique_genes <- unique(DE_results_list[[1]]$gene)
UPN23_cellhashing_unique_genes <- unique(DE_results_list[[3]]$gene)

display_venn(
  x = list(UPN23_non_cellhashing_unique_genes, UPN23_cellhashing_unique_genes),
  category.names = c("UPN23 non cellhashing", 
                     "UPN23 cellhashing"),
  # Cercles
  lwd = 2,
  lty = 'blank',
  fill = c("#999999", "#E69F00"),
  # Nombres
  cex = .9,
  fontface = "italic",
  # Noms des groupes
  cat.cex = 1,
  cat.fontface = "bold",
  cat.default.pos = "outer",
  cat.dist = c(0.055, 0.055)
)
```

##### Gene list common in both conditions

```{r}
datatable(data.frame(Common_genes = intersect(UPN23_non_cellhashing_unique_genes, UPN23_cellhashing_unique_genes)),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to non cell hashing

```{r}
datatable(data.frame(Non_cellhashing_genes = UPN23_non_cellhashing_unique_genes[!UPN23_non_cellhashing_unique_genes %in% UPN23_cellhashing_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to cell hashing

```{r}
datatable(data.frame(Cellhashing_genes = UPN23_cellhashing_unique_genes[!UPN23_cellhashing_unique_genes %in% UPN23_non_cellhashing_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

#### UPN29

```{r}
UPN29_non_cellhashing_unique_genes <- unique(DE_results_list[[2]]$gene)
UPN29_cellhashing_unique_genes <- unique(DE_results_list[[4]]$gene)

display_venn(
  x = list(UPN29_non_cellhashing_unique_genes, UPN29_cellhashing_unique_genes),
  category.names = c("UPN29 non cellhashing", 
                     "UPN29 cellhashing"),
  # Cercles
  lwd = 2,
  lty = 'blank',
  fill = c("#999999", "#E69F00"),
  # Nombres
  cex = .9,
  fontface = "italic",
  # Noms des groupes
  cat.cex = 1,
  cat.fontface = "bold",
  cat.default.pos = "outer",
  cat.dist = c(0.055, 0.055)
)
```

##### Gene list common in both conditions

```{r}
datatable(data.frame(Common_genes = intersect(UPN29_non_cellhashing_unique_genes, UPN29_cellhashing_unique_genes)),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to non cell hashing

```{r}
datatable(data.frame(Non_cellhashing_genes = UPN29_non_cellhashing_unique_genes[!UPN29_non_cellhashing_unique_genes %in% UPN29_cellhashing_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to cell hashing

```{r}
datatable(data.frame(Cellhashing_genes = UPN29_cellhashing_unique_genes[!UPN29_cellhashing_unique_genes %in% UPN29_non_cellhashing_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

#### UPN73

```{r}
UPN73_fixed_unique_genes <- unique(DE_results_list[[5]]$gene)
UPN73_cellhashing_unique_genes <- unique(DE_results_list[[7]]$gene)

display_venn(
  x = list(UPN73_fixed_unique_genes, UPN73_cellhashing_unique_genes),
  category.names = c("UPN73 fixed", 
                     "UPN73 cellhashing"),
  # Cercles
  lwd = 2,
  lty = 'blank',
  fill = c("#999999", "#E69F00"),
  # Nombres
  cex = .9,
  fontface = "italic",
  # Noms des groupes
  cat.cex = 1,
  cat.fontface = "bold",
  cat.default.pos = "outer",
  cat.dist = c(0.055, 0.055)
)
```

##### Gene list common in both conditions

```{r}
datatable(data.frame(Common_genes = intersect(UPN73_fixed_unique_genes, UPN73_cellhashing_unique_genes)),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to fixed cells

```{r}
datatable(data.frame(Non_cellhashing_genes = UPN73_fixed_unique_genes[!UPN73_fixed_unique_genes %in% UPN73_cellhashing_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to cell hashing

```{r}
datatable(data.frame(Cellhashing_genes = UPN73_cellhashing_unique_genes[!UPN73_cellhashing_unique_genes %in% UPN73_fixed_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

#### UPN78

```{r}
UPN78_fixed_unique_genes <- unique(DE_results_list[[6]]$gene)
UPN78_cellhashing_unique_genes <- unique(DE_results_list[[8]]$gene)

display_venn(
  x = list(UPN78_fixed_unique_genes, UPN78_cellhashing_unique_genes),
  category.names = c("UPN78 fixed", 
                     "UPN78 cellhashing"),
  # Cercles
  lwd = 2,
  lty = 'blank',
  fill = c("#999999", "#E69F00"),
  # Nombres
  cex = .9,
  fontface = "italic",
  # Noms des groupes
  cat.cex = 1,
  cat.fontface = "bold",
  cat.default.pos = "outer",
  cat.dist = c(0.055, 0.055)
)
```

##### Gene list common in both conditions

```{r}
datatable(data.frame(Common_genes = intersect(UPN78_fixed_unique_genes, UPN78_cellhashing_unique_genes)),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to fixed cells

```{r}
datatable(data.frame(Non_cellhashing_genes = UPN78_fixed_unique_genes[!UPN78_fixed_unique_genes %in% UPN78_cellhashing_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```

##### Gene list specific to cell hashing

```{r}
datatable(data.frame(Cellhashing_genes = UPN78_cellhashing_unique_genes[!UPN78_cellhashing_unique_genes %in% UPN78_fixed_unique_genes]),
  extensions = "Buttons", options = list(
    dom = "Bfrtip",
    buttons =
      list(list(
        extend = "collection",
        buttons = c("csv", "excel"),
        text = "Download"
      ))
  ))
```
