---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Results

## Summary

The following table give global information on datasets.

```{r}
DT::datatable(Result_table)
```

## Some QC plots for each sample

On the following plots, the sample is indicated in X axis.

Those plots show the distribution of the number of UMI (nUMI), the number of genes (ngenes) and the percentage of mitochondrial genes (percent_mito) in each cell (dot on plots).

### UPN23

```{r QC_UPN23}
Seurat_UPN23 <- compute_percent_mito_seurat(Seurat_UPN23, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
draw_QC_plots_seurat(Seurat_UPN23)
draw_QC_plots_seurat_no_dots(Seurat_UPN23)

draw_all_qc_plot_with_outlier(Seurat_UPN23, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN23_filtered <- subset(Seurat_UPN23, subset = ngenes_filter | nUMI_filter | percent_mito_filter, invert = T)
```

### UPN23 after filtering

```{r}
draw_QC_plots_seurat(Seurat_UPN23_filtered)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_filtered)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_filtered, 
                                 feature_to_plot = Seurat_UPN23_filtered@meta.data$nCount_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_filtered, 
                                 feature_to_plot = Seurat_UPN23_filtered@meta.data$nFeature_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_filtered, 
                                 feature_to_plot = Seurat_UPN23_filtered@meta.data$percent_mito)
```


### UPN29

```{r QC_UPN29}
Seurat_UPN29 <- compute_percent_mito_seurat(Seurat_UPN29, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
draw_QC_plots_seurat(Seurat_UPN29)
draw_QC_plots_seurat_no_dots(Seurat_UPN29)

draw_all_qc_plot_with_outlier(Seurat_UPN29, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN29_filtered <- subset(Seurat_UPN29, subset = ngenes_filter | nUMI_filter | percent_mito_filter, invert = T)
```

### UPN23 after filtering

```{r}
draw_QC_plots_seurat(Seurat_UPN29_filtered)
draw_QC_plots_seurat_no_dots(Seurat_UPN29_filtered)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN29_filtered, 
                                 feature_to_plot = Seurat_UPN29_filtered@meta.data$nCount_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN29_filtered, 
                                 feature_to_plot = Seurat_UPN29_filtered@meta.data$nFeature_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN29_filtered, 
                                 feature_to_plot = Seurat_UPN29_filtered@meta.data$percent_mito)
```

### UPN23 with cellhashing

```{r QC_UPN23_cellhashing}
Seurat_UPN23_UPN29_cellhashing_UPN23 <- compute_percent_mito_seurat(Seurat_UPN23_UPN29_cellhashing_UPN23, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
draw_QC_plots_seurat(Seurat_UPN23_UPN29_cellhashing_UPN23)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_UPN29_cellhashing_UPN23)

draw_all_qc_plot_with_outlier(Seurat_UPN23_UPN29_cellhashing_UPN23, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN23_UPN29_cellhashing_UPN23_filtered <- subset(Seurat_UPN23_UPN29_cellhashing_UPN23, subset = ngenes_filter | nUMI_filter | percent_mito_filter, invert = T)
```

### UPN23 cell hashing after filtering

```{r}
draw_QC_plots_seurat(Seurat_UPN23_UPN29_cellhashing_UPN23_filtered)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_UPN29_cellhashing_UPN23_filtered)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_UPN29_cellhashing_UPN23_filtered, 
                                 feature_to_plot = Seurat_UPN23_UPN29_cellhashing_UPN23_filtered@meta.data$nCount_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_UPN29_cellhashing_UPN23_filtered, 
                                 feature_to_plot = Seurat_UPN23_UPN29_cellhashing_UPN23_filtered@meta.data$nFeature_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_UPN29_cellhashing_UPN23_filtered, 
                                 feature_to_plot = Seurat_UPN23_UPN29_cellhashing_UPN23_filtered@meta.data$percent_mito)
```

### UPN29 with cellhashing

```{r QC_UPN29_cellhashing}
Seurat_UPN23_UPN29_cellhashing_UPN29 <- compute_percent_mito_seurat(Seurat_UPN23_UPN29_cellhashing_UPN29, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
draw_QC_plots_seurat(Seurat_UPN23_UPN29_cellhashing_UPN29)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_UPN29_cellhashing_UPN29)

draw_all_qc_plot_with_outlier(Seurat_UPN23_UPN29_cellhashing_UPN29, filter_numi = 20000, filter_ngenes = 4000, filter_percent_mito = 25)
Seurat_UPN23_UPN29_cellhashing_UPN29_filtered <- subset(Seurat_UPN23_UPN29_cellhashing_UPN29, subset = ngenes_filter | nUMI_filter | percent_mito_filter, invert = T)
```

### UPN29 cell hashing after filtering

```{r}
draw_QC_plots_seurat(Seurat_UPN23_UPN29_cellhashing_UPN29_filtered)
draw_QC_plots_seurat_no_dots(Seurat_UPN23_UPN29_cellhashing_UPN29_filtered)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_UPN29_cellhashing_UPN29_filtered, 
                                 feature_to_plot = Seurat_UPN23_UPN29_cellhashing_UPN29_filtered@meta.data$nCount_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_UPN29_cellhashing_UPN29_filtered, 
                                 feature_to_plot = Seurat_UPN23_UPN29_cellhashing_UPN29_filtered@meta.data$nFeature_RNA)
draw_QC_plot_seurat_with_boxplot(seurat_obj = Seurat_UPN23_UPN29_cellhashing_UPN29_filtered, 
                                 feature_to_plot = Seurat_UPN23_UPN29_cellhashing_UPN29_filtered@meta.data$percent_mito)
```