---
output: html_document
editor_options: 
  chunk_output_type: console
---

## Correlation between cell hashing and non cell hashing samples

### Plots using mean expression of all genes

For this plot, the mean expression of all genes is shown.

```{r}
# Get common genes in compared datasets
# UPN23_UPN29_tot_genes <- list(rownames(Seurat_UPN23_filtered@assays$RNA@data),
#                               rownames(Seurat_UPN29_filtered@assays$RNA@data),
#                               rownames(Seurat_UPN23_UPN29_cellhashing_UPN23_filtered@assays$RNA@data),
#                               rownames(Seurat_UPN23_UPN29_cellhashing_UPN29_filtered@assays$RNA@data))
# UPN23_UPN29_genes <- Reduce(f = intersect, x = UPN23_UPN29_tot_genes)

UPN23_UPN29_Seurat_list <- list(Seurat_UPN23_filtered, Seurat_UPN29_filtered, 
                                Seurat_UPN23_UPN29_cellhashing_UPN23_filtered, Seurat_UPN23_UPN29_cellhashing_UPN29_filtered)

# UPN23_UPN29_Seurat_list_UPN23_UPN29_genes <- lapply(UPN23_UPN29_Seurat_list, subset, features = UPN23_UPN29_genes)

UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized <- lapply(UPN23_UPN29_Seurat_list, normalize_seurat_object)

merged_seurat <- merge(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]], 
                       c(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]], 
                         UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]], 
                         UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]), 
                       add.cell.ids = c("UPN23", "UPN29", "UPN23_cellhashing", "UPN29_cellhashing"),
                       merge.data = T)

merged_seurat@meta.data$cell_id <- gsub(pattern = "_[ATGC].*", replacement = "",x = rownames(merged_seurat@meta.data))

na_length <- rep(0, nrow(merged_seurat))
mean_df <- data.frame(UPN23_noncellhashing = na_length, UPN29_noncellhashing = na_length,
                      UPN23_cellhashing = na_length, UPN29_cellhashing = na_length)
rownames(mean_df) <- rownames(merged_seurat)
mean_df$UPN23_noncellhashing  <- rowMeans(GetAssayData(merged_seurat[, grep("UPN23_", colnames(merged_seurat))]))
mean_df$UPN29_noncellhashing  <- rowMeans(GetAssayData(merged_seurat[, grep("UPN29_", colnames(merged_seurat))]))
mean_df$UPN23_cellhashing  <- rowMeans(GetAssayData(merged_seurat[, grep("UPN23_cellhashing", colnames(merged_seurat))]))
mean_df$UPN29_cellhashing  <- rowMeans(GetAssayData(merged_seurat[, grep("UPN29_cellhashing", colnames(merged_seurat))]))
# mean_df$UPN23_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]]@assays$RNA@data)
# mean_df$UPN29_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]]@assays$RNA@data)
# mean_df$UPN23_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]]@assays$RNA@data)
# mean_df$UPN29_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]@assays$RNA@data)
ggpairs(mean_df) + ggtitle("Scatter plot matrix of mean expression of all genes in all cells")
```

```{r}
rm(merged_seurat)
gc()
```


### Plots using mean expression of genes found in all samples

For this plot, I subset each sample to only common genes found in all samples.

```{r}
# Get common genes in compared datasets
UPN23_UPN29_tot_genes <- list(rownames(Seurat_UPN23_filtered@assays$RNA@data),
                              rownames(Seurat_UPN29_filtered@assays$RNA@data),
                              rownames(Seurat_UPN23_UPN29_cellhashing_UPN23_filtered@assays$RNA@data),
                              rownames(Seurat_UPN23_UPN29_cellhashing_UPN29_filtered@assays$RNA@data))
UPN23_UPN29_genes <- Reduce(f = intersect, x = UPN23_UPN29_tot_genes)

UPN23_UPN29_Seurat_list <- list(Seurat_UPN23_filtered, Seurat_UPN29_filtered, 
                                Seurat_UPN23_UPN29_cellhashing_UPN23_filtered, Seurat_UPN23_UPN29_cellhashing_UPN29_filtered)

UPN23_UPN29_Seurat_list_UPN23_UPN29_genes <- lapply(UPN23_UPN29_Seurat_list, subset, features = UPN23_UPN29_genes)

UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized <- lapply(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes, normalize_seurat_object)

na_length <- rep(NA, length(UPN23_UPN29_genes))
mean_df <- data.frame(UPN23_noncellhashing = na_length, UPN29_noncellhashing = na_length,
                      UPN23_cellhashing = na_length, UPN29_cellhashing = na_length)
mean_df$UPN23_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]]@assays$RNA@data)
mean_df$UPN29_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]]@assays$RNA@data)
mean_df$UPN23_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]]@assays$RNA@data)
mean_df$UPN29_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]@assays$RNA@data)
ggpairs(mean_df) + ggtitle("Scatter plot matrix of mean expression of each gene in all cells")
```

### Plots using mean expression of highly variable genes in all samples

On the following plot, We look at the correlation of expression value of the 2000 most variable genes in all samples.
I merged the 4 Seurat object (2 non cell hashing and 2 cellhashing) using the **merge** function. Then, I normalized and find the most variable genes.

```{r}
merged_seurat <- merge(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]], 
                       c(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]], 
                         UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]], 
                         UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]), 
                       add.cell.ids = c("UPN23", "UPN29", "UPN23_cellhashing", "UPN29_cellhashing"),
                       merge.data = F)

merged_seurat@meta.data$cell_id <- gsub(pattern = "_[ATGC].*", replacement = "",x = rownames(merged_seurat@meta.data))

merged_seurat <- perform_clustering_seurat(merged_seurat)

na_length <- rep(0, length(merged_seurat@assays$RNA@var.features))
mean_df <- data.frame(UPN23_noncellhashing = na_length, UPN29_noncellhashing = na_length,
                      UPN23_cellhashing = na_length, UPN29_cellhashing = na_length)
rownames(mean_df) <- merged_seurat@assays$RNA@var.features
mean_df$UPN23_noncellhashing  <- rowMeans(GetAssayData(merged_seurat[merged_seurat@assays$RNA@var.features, 
                                                                     grep("UPN23_", colnames(merged_seurat))]))
mean_df$UPN29_noncellhashing  <- rowMeans(GetAssayData(merged_seurat[merged_seurat@assays$RNA@var.features, 
                                                                     grep("UPN29_", colnames(merged_seurat))]))
mean_df$UPN23_cellhashing  <- rowMeans(GetAssayData(merged_seurat[merged_seurat@assays$RNA@var.features, 
                                                                  grep("UPN23_cellhashing", colnames(merged_seurat))]))
mean_df$UPN29_cellhashing  <- rowMeans(GetAssayData(merged_seurat[merged_seurat@assays$RNA@var.features, 
                                                                  grep("UPN29_cellhashing", colnames(merged_seurat))]))
# mean_df$UPN23_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]]@assays$RNA@data)
# mean_df$UPN29_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]]@assays$RNA@data)
# mean_df$UPN23_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]]@assays$RNA@data)
# mean_df$UPN29_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]@assays$RNA@data)
ggpairs(mean_df) + ggtitle("Scatter plot matrix of mean expression of all genes in all cells")
```

```{r}
rm(merged_seurat)
gc()
```


### Plots using mean expression of highly variable genes extracted from all samples

On the following plot, We look at the correlation of expression value of the 2000 most variable genes extracted from all samples.
I retrieve the variable genes from all samples, merged the 4 seurat object and use the variable genes list to draw the correlation plot. The gene list was subset to the intersection of the 4 variable gene lists.

```{r}
UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered <- lapply(X = UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized, FUN = perform_clustering_seurat)

var_genes_list <- lapply(UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered, function(x){print(x$RNA@var.features)})
# var_genes_list_intersect <- Reduce(f = union, x = var_genes_list)
var_genes_list_intersect <- Reduce(f = intersect, x = var_genes_list)

merged_seurat <- merge(UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered[[1]], 
                       c(UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered[[2]], 
                         UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered[[3]], 
                         UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered[[4]]), 
                       add.cell.ids = c("UPN23", "UPN29", "UPN23_cellhashing", "UPN29_cellhashing"),
                       merge.data = F)

merged_seurat@meta.data$cell_id <- gsub(pattern = "_[ATGC].*", replacement = "",x = rownames(merged_seurat@meta.data))

# merged_seurat <- perform_clustering_seurat(merged_seurat)
```

Using this method, we retrieve `r length(var_genes_list_intersect)` genes which are in the union of variable genes between the 4 samples. After computing the mean expression between each sample, we can draw the following plot.

```{r}
na_length <- rep(0, length(var_genes_list_intersect))
mean_df <- data.frame(UPN23_noncellhashing = na_length, UPN29_noncellhashing = na_length,
                      UPN23_cellhashing = na_length, UPN29_cellhashing = na_length)
rownames(mean_df) <- var_genes_list_intersect
mean_df$UPN23_noncellhashing  <- rowMeans(GetAssayData(merged_seurat[var_genes_list_intersect, 
                                                                     grep("UPN23_", colnames(merged_seurat))]))
mean_df$UPN29_noncellhashing  <- rowMeans(GetAssayData(merged_seurat[var_genes_list_intersect, 
                                                                     grep("UPN29_", colnames(merged_seurat))]))
mean_df$UPN23_cellhashing  <- rowMeans(GetAssayData(merged_seurat[var_genes_list_intersect, 
                                                                  grep("UPN23_cellhashing", colnames(merged_seurat))]))
mean_df$UPN29_cellhashing  <- rowMeans(GetAssayData(merged_seurat[var_genes_list_intersect, 
                                                                  grep("UPN29_cellhashing", colnames(merged_seurat))]))
# mean_df$UPN23_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]]@assays$RNA@data)
# mean_df$UPN29_noncellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]]@assays$RNA@data)
# mean_df$UPN23_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]]@assays$RNA@data)
# mean_df$UPN29_cellhashing <- rowMeans(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]@assays$RNA@data)
ggpairs(mean_df) + ggtitle("Scatter plot matrix of mean expression of all genes in all cells")
```

We can draw the venn diagramm of all variable genes found in the 4 samples to better see what happened.

```{r}
names(var_genes_list) <- c("UPN23", "UPN29", "UPN23_cellhashing", "UPN29_cellhashing")

display_venn(
  x = var_genes_list,
  category.names = c("UPN23", "UPN29", "UPN23_cellhashing", "UPN29_cellhashing"),
  # Cercles
  lwd = 2,
  lty = 'blank',
  fill = c("grey", "#E69F00", "#999999", "orange"),
  # Nombres
  cex = .9,
  fontface = "italic",
  # Noms des groupes
  cat.cex = 1,
  cat.fontface = "bold",
  cat.default.pos = "outer",
  cat.dist = c(0.055, 0.055, 0.055, 0.055)
)
```

#### Table of all variable genes

Here is a table of the 2000 variable genes found in each sample

```{r}
datatable(as.data.frame(var_genes_list))
```

#### Table of common variable genes

Here is a table of the `r length(var_genes_list_intersect)` variable genes found common in all sample.

```{r}
datatable(as.data.frame(var_genes_list_intersect))
```

<!-- ### Plots using random cells -->

<!-- For the following plots, I chose random cells to draw gene expression. -->

<!-- ```{r} -->
<!-- # Generate 10 random number between 1 and the min number of cell in compared datasets -->
<!-- for(random in sample(1:min(sapply(UPN23_UPN29_Seurat_list, ncol)), 10)){ -->
<!--   na_length <- rep(NA, length(UPN23_UPN29_genes)) -->
<!--   loop_df <- data.frame(UPN23_noncellhashing = na_length, UPN29_noncellhashing = na_length, -->
<!--                         UPN23_cellhashing = na_length, UPN29_cellhashing = na_length, row.names = UPN23_UPN29_genes) -->
<!--   loop_df$UPN23_noncellhashing <- UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[1]]@assays$RNA@data[, random] -->
<!--   loop_df$UPN29_noncellhashing <- UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[2]]@assays$RNA@data[, random] -->
<!--   loop_df$UPN23_cellhashing <- UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[3]]@assays$RNA@data[, random] -->
<!--   loop_df$UPN29_cellhashing <- UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized[[4]]@assays$RNA@data[, random] -->
<!--   print(ggpairs(loop_df) + ggtitle("Scatter plot matrix of expression of each gene randomly selected cells")) -->
<!-- } -->
<!-- ``` -->

```{r}
#Clean memory
rm(UPN23_UPN29_Seurat_list_UPN23_UPN29_genes_normalized,
   UPN23_UPN29_Seurat_list_UPN23_UPN29_genes,
   UPN23_UPN29_Seurat_list, merged_seurat)
rm(mean_df, UPN23_UPN29_Seurat_list_UPN23_UPN29_clustered)
rm(var_genes_list_intersect, var_genes_list)
# rm(Seurat_UPN23_UPN29_cellhashing, Seurat_UPN23_UPN29_cellhashing_UPN23, Seurat_UPN23_UPN29_cellhashing_UPN29)
rm(UPN23, UPN29, UPN23_UPN29_cellhashing)
gc()
```